\documentclass[margin,line]{res}
\usepackage{hyperref}
%\hypersetup{hidelinks} % Link colors
\usepackage[utf8x]{inputenc}


\begin{document}
\name{\Large Vikesh Kumar Tiwari}

\begin{resume}

\section{Contact\\Information}  
E-mail: tvicky002@gmail.com\\
Phone: (+91)9930-631-359\\
Website: \url{http://vicky002.github.io}\\



\section{Education}
Sardar Patel Institute of Technology - Information Technology\\
2013 - 2017(expected)\\

\section{Projects}
\begin{itemize} \itemsep -4pt
\item \textbf{C++ and Algorithms Sublime Text Package }\\
Sublime C++ and Algorithms code snippets. Uses C++ \& JavaScript. \\
\url{http://goo.gl/MbQKgR/}\\

\item \textbf{FlagQuiz Android App}\\
A simple andorid game in which there are 10 Quizzes and user have to guess from 3 options. There are additional features like select particular region, show more options and select country region. Uses Java \& Android.\\
 \url{http://goo.gl/NKXJ5q/}\\

\item \textbf{AlgoWiki - All CS resources at one place.}\\
On Internet, There is a lot of knowledge on different topics scarred over different sources. Most of the knowledge is
either online on the web or with the people as human knowledge. AlgoWiki is a platform to bind this scattered piece of knowledge at one place. \\
\url{http://www.algowiki.in}\\

\item\textbf{HTML5 Music Player}\\
Music Player, Drag and Drop Mp3 files and user can also search select and remove files. It also supports shuffle and repeat options. Once the web page is loaded, player works without internet connection.\\
code : \url{https://goo.gl/whKjZ3}\\ 
wepage : \url{https://myfirstplayer.herokuapp.com/}\\

\end{itemize}



\section{Experience}
\begin{itemize} \itemsep -4pt

\item\textbf{Directi, Software Engineering Intern, March 2015 to September 2015}\\
Worked in CodeChef Department. CodeChef is non-profit educational initiative by Directi to help students and professionals test and improve their coding skills. Apart from this, it aims to reach out to students while they are young and inculcate a culture of programming in India\\
- Worked on Online Compiler Test Data Judge. Uses C++. \\
- CodeChef Learning Module website for kids. Uses Python-Django.\\
- Collecting Education Resources. Uses Python.

\end{itemize}

\section{Additional Experience}
\begin{itemize} \itemsep -4pt
 \item\textbf{Technical Head - Information Technology Student's Association, SPIT }\\
As a Technical Head I was involved in all the technical events of College. Organizing Technical Events and workshops in college. I was also a part of college web team.\\

 
 \item\textbf{ChairPerson -  SPIT Coder's Club}\\
Started Coder's Club in college to promote Programming and Open source development. Started Monthly Coding Contest series, to help students learn and improve programming skills. Started 60 Days open source development challenge to develop open source projects in 60 days.\\
- Blog: \url{http://spitcoderclub.blogspot.in/}
\\
\item\textbf{CodeChef Campus Representative}\\
Worked as Campus Representative for CodeChef, to promote competitive programming and CodeChef Contests in college.
\end{itemize}


\section{Languanges and Tools}
C, C++, Python, Django, PHP, HTML, CSS, JS, SQL,.\\
Nginx, Apache Web server, Advanced Linux.\\ 
Git, Vim, Sublime, PhpStorm, Android Studio, Eclipse.\\
Slack, Trello, IRC.\\


\section{Extra-Curricular \& Achievements}

\begin{itemize} \itemsep -4pt
 \item My ream ranked 128th in IEEE Xtreme Programming, 2013.\\
 \item My team ranked 108th in IEEE Xtreme Programming, 2014. \\
 \item Active Participant in Competitive Programming and Other Coding Competitions. \\
 - Ranked 3rd in DJ Shaghvi College Techfest Coding Competition.\\
 - Current World rank 5113 among 303030 registered users on Sphere Online Judge. \\
 - Current World rank 5318 among 45000+ active programmers on CodeChef.\\
 - Active participant in other coding platforms Hackerearth, Hackerrank, USACO and CodeForces.\\
 \item Most viewed writer on Quora of topic Introduction to Algorithm.  
\end{itemize}




\section{Web Presence}
\begin{itemize} \itemsep -4pt
 \item Quora (I write and read) : \url{https://www.quora.com/Vikesh-Tiwari}\\
 \item GitHub (I share my code) : \url{https://github.com/vicky002}\\
 \item Blog (I share my experiences) : \\ 
 - \url{https://prmgevryday.quora.com/}\\
 - \url{http://vicky002.github.io/myblog}\\
 - \url{http://topblogcoder.blogspot.in/}\\
 \item Online Web Presence with name : \textbf{vicky002}, \url{https://goo.gl/I9kSp3}\\
\end{itemize}







\end{resume}
\end{document}
